Rank Verification for Exponential Families

### 2016-09-29 verifying-winner.tex
underfull hbox fixed

\begin{lemma}~\\
\begin{enumerate}
\item Suppose $\left(x_1, x_2, x_3, \ldots\right)$ and $\left(x_1, y_2, y_3, \ldots\right)$ are two vectors in $\RR^n$. Then
$$\left(x_1, x_2, x_3, \ldots\right) \succeq \left(x_1, y_2, y_3, \ldots\right) \text{ if and only if } \left(x_2, x_3, \ldots\right) \succeq \left(y_2, y_3, \ldots\right).$$
\item (Principle of transfer) If $x_1 > x_2$ and $t \ge 0$, then
$$\left(x_1 + t, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2 + t, x_3, \ldots\right).$$
If $t \le 0$, the majorization is reversed.
\end{enumerate}
\label{lma:twoprop}
\end{lemma}

\begin{proof}~\\
\begin{enumerate}
\item The property follows from an equivalent formulation of majorization listed in \citet{Marshall:2010hb}, where $x \succeq y$ if and only if
$$\sum_{j=1}^n x_n = \sum_{j=1}^n y_n \quad \text{ and } \quad \sum_{j=1}^n \left(x_j - a\right)_+ \ge \sum_{j=1}^n \left(y_j - a\right)_+ \text{ for all } a \in \RR.$$

@@

Following the framework in \citet{Fithian:2014ws}, we first construct the p-values by conditioning on the selection event where the winner is $1$: 
$$A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.$$
For convenience, we let
$$D_{jk} = \frac{X_j - X_k}{2} \quad \text{ and } \quad M_{jk} = \frac{X_j + X_k}{2}.$$

@@

Before conditioning on $A_1$, the distribution in \label{eq:condlaw} is symmetric around 0 under $\theta_1=\theta_j$. Since the denominator of $p_{12}$ integrates over half of this symmetric distribution, it is always equal to $1/2$. Thus, the one-sided conditional test at level $\alpha$ is equivalent to the one-sided unadjusted test at level $\alpha/2$, or equivalently the two-sided unadjusted pairwise test at level $\alpha$.

>>>>

\begin{lemma}\leavevmode
\begin{enumerate}
\item Suppose $\left(x_1, x_2, x_3, \ldots\right)$ and $\left(x_1, y_2, y_3, \ldots\right)$ are two vectors in $\RR^n$. Then
$$\left(x_1, x_2, x_3, \ldots\right) \succeq \left(x_1, y_2, y_3, \ldots\right) \text{ if and only if } \left(x_2, x_3, \ldots\right) \succeq \left(y_2, y_3, \ldots\right).$$
\item (Principle of transfer) If $x_1 > x_2$ and $t \ge 0$, then
$$\left(x_1 + t, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2 + t, x_3, \ldots\right).$$
If $t \le 0$, the majorization is reversed.
\end{enumerate}
\label{lma:twoprop}
\end{lemma}

\begin{proof}\leavevmode
\begin{enumerate}
\item The property follows from an equivalent formulation of majorization listed in \citet{Marshall:2010hb}, where $x \succeq y$ if and only if
$$\sum_{j=1}^n x_n = \sum_{j=1}^n y_n \quad \text{ and } \quad \sum_{j=1}^n \left(x_j - a\right)_+ \ge \sum_{j=1}^n \left(y_j - a\right)_+ \text{ for all } a \in \RR.$$

@@

Following the framework in \citet{Fithian:2014ws}, we first construct the $p$-values by conditioning on the selection event where the winner is $1$: 
$$A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.$$
For convenience, we let
$$D_{jk} = \frac{X_j - X_k}{2} \quad \text{ and } \quad M_{jk} = \frac{X_j + X_k}{2}.$$

@@

Before conditioning on $A_1$, the distribution in \eqref{eq:condlaw} is symmetric around $0$ under $\theta_1=\theta_j$. Since the denominator of $p_{12}$ integrates over half of this symmetric distribution, it is always equal to $1/2$. Thus, the one-sided conditional test at level $\alpha$ is equivalent to the one-sided unadjusted test at level $\alpha/2$, or equivalently the two-sided unadjusted pairwise test at level $\alpha$.
